--- 
title: "Анализ данных в биомедицинских исследованиях"
author: |
  `r ifelse(knitr::is_latex_output(), 
  "Суворов Александр Юрьевич\\\\Вергун Мария Андреевна", 
  "Суворов Александр Юрьевич<br>Вергун Мария Андреевна")`
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output:
  bookdown::gitbook:
    css: style.css # Include a custom CSS file for font settings
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
fontsize: '12pt'
monofont: "Source Code Pro"
monofontoptions: "Scale=0.85"
link-citations: yes
github-repo: rstudio/bookdown-demo
description: "This is a minimal example of using the bookdown package to write a book. The output format for this example is bookdown::gitbook."
---

<!-- bookdown::render_book(output_dir = './docs', clean = TRUE) -->
<!-- ```{r include=FALSE}
source("generate_bookdown_yml.R")


``` -->

# Prerequisites

This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

The **bookdown** package can be installed from CRAN or Github :

```{r eval=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.org/tinytex/>.

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
